### 2020-08-25 manuscript/PLOS-MSc-Thesis.tex
extend abstract methods section

\subsection*{Methods}
In this study we used a genetic algorithm in order to explore the genotypic 
space of GRNs capable of producing a band expression pattern in a group of 
cells.

>>>>

\subsection*{Methods}
In this study we used a genetic algorithm in order to explore the genotypic 
space of three-node GRNs capable of producing a band expression pattern in a 
group of cells. In contrast to previous studies, we explore multiple input 
network designs that enable more morphogen interpretation mechanisms to arise.
